
---
title: "SVM_Homework"
output:	html_document
author: "Han Sun"
date: "`r Sys.Date()`"
---


```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("rmarkdown")
library("knitr")
```

# Problem 1

1. Choose a Problem from Analytic 2 or from an internet repositories.
2. Compute a SVM and a model from Analytic 1 or 2. Compare both analysis. Compare the confusion matrices.Differences?
3. Present your results.

# Loading libraries

```{r setup, include=FALSE}
library(ggplot2)
library(rpart)
library(rpart.plot)
library(gmodels)
library(e1071)
library(gridExtra)
library(randomForest)
data(iris)
summary(iris)
```

# Loading dataset

```{r dataset}
data(iris)
summary(iris)
```

# Data Pre-processing

```{r data pre-processing}
temp = as.data.frame(scale(iris[,1:4]))
temp$Species = iris$Species
summary(temp)
```

# Creating training and testing dataset

```{r create training and testing dataset}
smp_size =  100
set.seed(123)
train_ind = sample(seq_len(nrow(temp)), size = smp_size)
train = temp[train_ind, ]
test = temp[-train_ind, ]
```

# Classification Techniques

# 1. Decision Tree

```{r decision tree}
model.rpart = rpart(Species ~ . ,data =train)
preds.rpart = predict(model.rpart,newdata = test,type = "class")
```

# CrossTable: Confusion Matrix

```{r matrix_decision_tree}
CrossTable(test$Species,preds.rpart,chisq = F,prop.r = F,prop.c = F,prop.t = F,prop.chisq = F)

```

# Accuracy of Decision trees

```{r accuracy_decision_tree}
((16+20+12)/nrow(test))
```

# 2. k-Nearest Neighbours

```{r k-nearest neighbours}
library(class)
cl = train$Species
set.seed(1234)
preds.knn = knn(train[,1:4],test[,1:4],cl,k=3)
```

# CrossTable: Confusion Matrix

```{r matrix_k}
CrossTable(preds.knn,test$Species,chisq = F,prop.r = F,prop.c = F,prop.t = F,prop.chisq = F)
```

# Accuracy of k-Nearest Neighbours

```{r accuracy_k}
((16+18+12)/nrow(test))
```

# 3. Support Vector Machine(SVM)

```{r svm}
model.svm = svm(Species ~ . ,data = train)
preds.svm = predict(model.svm,newdata = test)
```

# CrossTable: Confusion Matrix

```{r matrix_svm}
CrossTable(preds.svm,test$Species,chisq = F,prop.r = F,prop.c = F,prop.t = F,prop.chisq = F)

```

# Accuracy of SVM

```{r accuracy_svm}
((16+20+13)/nrow(test))
```

# 4.Random Forest

```{r random forest}
set.seed(100)
model.rf = randomForest(Species ~ .,data = train)
preds.rf = predict(model.rf,newdata = test)
```

# CrossTable: Confusion Matrix

```{r matrix_random_forest}
CrossTable(preds.rf,test$Species,chisq = F,prop.r = F,prop.c = F,prop.t = F,prop.chisq = F)
```

# Accuracy of Random Forest

```{r accuracy_random_forestE}
((16+19+13)/nrow(test))
```

# Accuracy comparison

```{r accuracy comparison}
models = data.frame(Technique = c("Decision Tree","kNN","SVM","Random Forest"),Accuracy_Percentage = c(0.96,0.92,0.98,0.96))
models
```
